---
title: "Correlation and regression analysis example"
output: 
  html_document: 
    theme: paper
    toc: yes
    toc_float: yes
  html_notebook: 
    toc: yes
    toc_float: yes
---

# Problem

Load the data set **cats** from the "MASS" library, which contains information on various anatomical features of house cats.

```{r catsdata}
library(MASS)
data(cats)
```

"Bwt" is the body weight in kilograms, "Hwt" is the heart weight in grams, and "Sex" should be obvious. There are no missing values in any of the variables.

* Have a look at the data set.
* Plot a data (scatterplot of Bwt and Hwt)
* Are "Bwt" and "Hwt" correlated? Test for correlation - use the Pearson correlation coefficient.
* Does "Hwt" depends on "Bwt"? Plot the regression line and then use appropriate plots to check for model assumptions.
* Comment on the diagnostic plots.

# Solution

```{r}
head(cats)
str(cats)
plot(cats$Bwt, cats$Hwt)
plot(Hwt ~ Bwt, data=cats) #to get the ~ you can search lm in help cuz they have it (just copy paste it)

cor(cats$Bwt, cats$Hwt) #coefficiente di correlazione (vicino a 1=correlate)
cor.test(cats$Bwt, cats$Hwt) #gives t-test too (it matters here cuz p-value<0.5 means it true, they correlated)
#You can switch the variables in the cor function and nothing changes


```

```{r}
#to add this chunk you just gotta click the c+ button and choose R
mod <- lm(Hwt ~ Bwt, data=cats) #it is also ok to write cats$Bwt but inconvenient if you gotta reuse the formula
summary(mod) #we see in "intercept - estimate std." that for every bwt+1,you get hwtx4
```
```{r}
plot(cats$Bwt, cats$Hwt)
abline(coef(mod), col="red")

```

```{r}
par(mfrow=c(2,2)) #this is to tell R we want to see the graphs on to 2 rows and 2 columns
plot(mod)

#ASSUNTI:
#correlazioni dei residui - primo grafico (no andamenti strani)
#normalità dei residui - secondo grafico (distribuzione su una retta)
#omogeneità della varianza dei residui - terzo grafico (più o meno stessa dispersione per i vari valori di x)

#quarto grafico è per verificare che non ci siano dati particolarmente influenti sull'analisi di regresione) (nuvola di cook, gott see what is inside-outside)
```



